FTLR proof cases

### 2018-06-27 fully-abstract-comp/ftlr-proof-cases.tex
Prove another splicing lemma.
Prove the splicing-related stuff in the FTLR case 5.

\begin{lemma}[Capability splicing retains safety for stack capabilities]
  \label{lem:splitting-safety-stack}
  If
  \begin{itemize}
  \item $\npair{(c_{1,S},c_{1,T})} \in \lrvg{\trust}(W_1)$
  \item $\npair{(c_{2,S},c_{2,T})} \in \lrvg{\trust}(W_2)$
  \item $b \le n \le e$
  \item $c_{1,S} = \stkptr{\perm,\baddr,n,\aaddr}$
  \item $c_{1,T} = ((\perm,\linear),\baddr,n,\aaddr)$
  \item $c_{2,S} = \stkptr{\perm,n,\eaddr,\aaddr}$
  \item $c_{2,T} = ((\perm,\linear),n,\eaddr,\aaddr)$
  \item $c_S = \stkptr{\perm,\baddr,\eaddr,\aaddr}$
  \item $c_T = ((\perm,\linear),\baddr,\eaddr,\aaddr)$
  \item $c_{1,S}' = c_{1,T}' = 0$
  \item $c_{2,S}' = c_{2,T}' = 0$
  \end{itemize}
  then there exist $W_1',W_2',W_3'$ such that
  \begin{itemize}
  \item $W_1 \oplus W_2 = W_1' \oplus W_2' \oplus W_3'$
  \item $\npair{(c_S,c_T)} \in \lrvg{\trust}(W_3')$
  \item $\npair{(c_{1,S}',c_{1,T}')} \in \lrvg{\trust}(W_1')$
  \item $\npair{(c_{2,S}',c_{2,T}')} \in \lrvg{\trust}(W_2')$
  \end{itemize}
\end{lemma}
\begin{proof}
  TODO
\end{proof}

@@

    From $\npair{(\Phi_S(r_3),\Phi_S(r_3))} \in \lrvg{\trust}(R_R(r_3))$, Lemma~\ref{lem:splitting-safety-stack} gives us $W_1$, $W_2$ and $W_3$ such that $R_R(r_3) = W_1 \oplus W_2 \oplus W_3$ and $\npair{(w_1,w_1) \in \lrvg{\trust}(W_1)}$, $\npair{(w_2,w_2) \in \lrvg{\trust}(W_2)}$ and $\npair{(w_3,w_3) \in \lrvg{\trust}(W_3)}$.
    We take $R_R'(r_1) = W_1$, $R_R'(r_2) = W_2$ and $R_R'(r_3) = W_3 \oplus R_R(r_1) \oplus R_R(r_2)$ and $R_R' = R_R(r)$ elsewhere.

@@

TODO
  \item Case \ref{case:ftlr:move-cca-etc:splice-normal}:

TODO
  \item Case \label{case:ftlr:move-cca-etc:splice-seal}:

@@

  By Lemma~\ref{lem:lro-anti-red-gen} it suffices to show
  \[
    \npair[n-1]{\Phi_S',\Phi_T'} \in \lro
  \]
  which follows from the induction hypothesis in the case where $\Phi_S'.\reg(\pcreg) = ((\rx,\normal),\baddr,\eaddr,\_)$.
  In this case, the IH is applicable because we have the following:
  \begin{itemize}
  \item One of the following sets of requirements holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S'$ is reasonable up to $n-1$ steps and $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \untrusted$, $[b,e] \mathrel{\#} \ta$ and $\npair[n-1]{[\baddr,\eaddr]} \in \readCond{\normal,W_\pcreg}$
    \end{itemize}

>>>>

\begin{lemma}[Capability splicing retains safety for stack capabilities]
  \label{lem:splicing-safety-stack}
  If
  \begin{itemize}
  \item $\npair{(c_{1,S},c_{1,T})} \in \lrvg{\trust}(W_1)$
  \item $\npair{(c_{2,S},c_{2,T})} \in \lrvg{\trust}(W_2)$
  \item $b \le m \le e$
  \item $c_{1,S} = \stkptr{\perm,\baddr,m,\aaddr}$
  \item $c_{1,T} = ((\perm,\linear),\baddr,m,\aaddr)$
  \item $c_{2,S} = \stkptr{\perm,m+1,\eaddr,\aaddr}$
  \item $c_{2,T} = ((\perm,\linear),m+1,\eaddr,\aaddr)$
  \item $c_S = \stkptr{\perm,\baddr,\eaddr,\aaddr}$
  \item $c_T = ((\perm,\linear),\baddr,\eaddr,\aaddr)$
  \end{itemize}
  then we have that
  \begin{itemize}
  \item $\npair{(c_S,c_T)} \in \lrvg{\trust}(W_1 \oplus W_2)$
  \end{itemize}
\end{lemma}
\begin{proof}
  This follows easily by definition of $\lrv$ and using Lemma~\ref{lem:conds-splicable}.
\end{proof}

@@

    From $\npair{(\Phi_S(r_3),\Phi_T(r_3))} \in \lrvg{\trust}(R_R(r_3))$, Lemma~\ref{lem:splitting-safety-stack} gives us $W_1$, $W_2$ and $W_3$ such that $R_R(r_3) = W_1 \oplus W_2 \oplus W_3$ and $\npair{(w_1,w_1) \in \lrvg{\trust}(W_1)}$, $\npair{(w_2,w_2) \in \lrvg{\trust}(W_2)}$ and $\npair{(w_3,w_3) \in \lrvg{\trust}(W_3)}$.
    We take $R_R'(r_1) = W_1$, $R_R'(r_2) = W_2$ and $R_R'(r_3) = W_3 \oplus R_R(r_1) \oplus R_R(r_2)$ and $R_R' = R_R(r)$ elsewhere.

@@

    From $\npair{(\Phi_S(r_2),\Phi_T(r_2))} \in \lrvg{\trust}(R_R(r_2))$ and $\npair{(\Phi_S(r_3),\Phi_T(r_3))} \in \lrvg{\trust}(R_R(r_3))$, Lemma~\ref{lem:splicing-safety-stack} tells us that $\npair{(w_1,w_1) \in \lrvg{\trust}(R_R(r_2)\oplus R_R(r_3))}$.
    Since $w_2 = w_2'=w_3=w_3'=0$, it's clear that 
    $\npair{(w_2,w_2') \in \lrvg{\trust}(R_R(r_1))}$ and $\npair{(w_3,w_3') \in \lrvg{\trust}(\purePart{R_R(r_3)})}$.
    We take $R_R'(r_1) = R_R(r_2)\oplus R_R(r_3)$, $R_R'(r_2) = R_R(r_1)$ and $R_R'(r_3) = \purePart{R_R(r_3)}$ and $R_R' = R_R(r)$ elsewhere.

  \item Case \ref{case:ftlr:move-cca-etc:splice-normal}:

    From $\npair{(\Phi_S(r_2),\Phi_T(r_2))} \in \lrvg{\trust}(R_R(r_2))$ and $\npair{(\Phi_S(r_3),\Phi_T(r_3))} \in \lrvg{\trust}(R_R(r_3))$, Lemma~\ref{lem:splicing-safety-normal} gives us $W_1',W_2',W_3'$ such that $R_R(r_2)\oplus R_R(r_3) = W_1'\oplus W_2' \oplus W_3'$ and
    $\npair{(w_i,w_i) \in \lrvg{\trust}(W_i')}$ for $i = 1,2,3$.
    We take $R_R'(r_1) = W_1'\oplus R_R(r_1)$ (which is defined because $R_R(r_1) \oplus (R_R(r_2)\oplus R_R(r_3))$ is defined), $R_R'(r_2) = W_2'$ and $R_R'(r_3) = W_3'$ and $R_R' = R_R(r)$ elsewhere.

  \item Case \label{case:ftlr:move-cca-etc:splice-seal}:

@@

  By Lemma~\ref{lem:lro-anti-red-gen} it suffices to show
  \[
    \npair[n-1]{\Phi_S',\Phi_T'} \in \lro
  \]
  which follows from the induction hypothesis.
  In this case, the IH is applicable because we have the following:
  \begin{itemize}
  \item One of the following sets of requirements holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S'$ is reasonable up to $n-1$ steps and $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \untrusted$, $[b,e] \mathrel{\#} \ta$ and $\npair[n-1]{[\baddr,\eaddr]} \in \readCond{\normal,W_\pcreg}$
    \end{itemize}
